### 2015-02-14 docs/report/array_sharing.tex
Added array merge section

\subsection{Copying \ttarray{}s}
Sections 22.2 and 24.1 of the ECMAScript 6 draft \cite{es6} specify the API for \ttarray{} and \tabuffer{} objects respectively. Some of the exposed operations provide a way to copy the contents of an \tabuffer{} into another \tabuffer{}, so they are to be considered as viable alternatives for the copy operation. Other alternatives to consider are:
\begin{itemize}
  \item Implementing a non-native function that copies the array elements one by one
  \item Using a \code{Blob} to store the contents of a \ttarray{} and reading the \code{Blob}'s contents into a new \ttarray{}.
\end{itemize}

>>>>

\subsection{Copying \ttarray{}s}
\label{subsec:copying-typed-arrays}
Sections 22.2 and 24.1 of the ECMAScript 6 draft \cite{es6} specify the API for \ttarray{} and \tabuffer{} objects respectively. Some of the exposed operations provide a way to copy the contents of an \tabuffer{} into another \tabuffer{}, so they are to be considered as viable alternatives for the copy operation. Other alternatives to consider are:
\begin{itemize}
  \item Implementing a non-native function that copies the array elements one by one
  \item Using a \code{Blob} to store the contents of a \ttarray{} and reading the \code{Blob}'s contents into a new \ttarray{}.
\end{itemize}
